Optimal Sizing of Stand-alone Solar PV Systems Through Automated Formal Synthesis Method

### 2019-09-22 Tex/IEEE_TOSE/trindade_IEEETOSE_rev0.tex
revised abstract
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

% As a general rule, do not put math, special symbols or citations
% in the abstract or keywords.
\begin{abstract}
There exist various methods and computer tools to size solar photovoltaic systems; however, those tools are mainly based on simulations, which do not cover all aspects of the design-space during the search for the optimal solution. In prior studies related to optimal sizing of photovoltaic systems, the focus was always on criteria or objectives. Here, we present a novel sound and automated approach to obtain optimal sizing of stand-alone photovoltaic systems using an unprecedented program synthesis. In particular, our variant of counterexample guided inductive synthesis (CEGIS) approach has two phases: first we synthesize the sizing of stand-alone photovoltaic systems based on power reliability, but that may not achieve the lowest cost; second, the proposed solution is then verified iteratively with a lower bound cost via symbolic model checking. If the verification step does not fail, the lower bound is adjusted; and if it fails, a counterexample is provided with the optimal sizing, thereby linking the technical response of the first phase with cost analysis of the second phase. Commercial equipment data from different manufacturers are provided to our synthesis engine and candidate solutions are derived from financial analysis. Experimental results using seven case studies show that our synthesis method is able to produce within an acceptable run-time the optimal system sizing. We also present a comparative with a specialized simulation tool over real photovoltaic systems to show the effectiveness of our approach, which is able to provide more detailed and accurate solution than the existing simulation tool.
\end{abstract}

@@

\begin{figure}[h]
\includegraphics[width=0.5\textwidth]{optimalsizingprocess2}
\centering
\caption{Comparative of optimal sizing methods}
\label{fig:optimization}
\end{figure}

>>>>

% As a general rule, do not put math, special symbols or citations
% in the abstract or keywords.
\begin{abstract}
There exist various methods and computer tools to size solar photovoltaic systems; however, these tools rely on simulations, which do not cover all aspects of the design space during the search for the optimal solution. In prior studies related to optimal sizing of photovoltaic systems, the focus was always on criteria or objectives. Here, we present a new sound and automated approach to obtain optimal sizing of stand-alone photovoltaic systems using an unprecedented program synthesis. In particular, our variant of counterexample guided inductive synthesis (CEGIS) approach has two phases: first we synthesize the sizing of stand-alone photovoltaic systems based on power reliability, but that may not achieve the lowest cost; second, the proposed solution is then verified iteratively with a lower bound cost via symbolic model checking. If the verification step does not fail, the lower bound is adjusted; and if it fails, a counterexample is provided with the optimal sizing, thereby linking the technical response of the first phase with cost analysis of the second phase. We provide commercial equipment data from different manufacturers to our synthesis engine and derive candidate solutions from financial analysis. Experimental results using seven case studies show that our synthesis method can produce within an acceptable run-time the optimal system sizing. We also present a comparative with a specialized simulation tool over real photovoltaic systems to show the effectiveness of our approach, which can provide a more detailed and accurate solution than that existing simulation tool.
\end{abstract}

@@

\begin{figure}[h]
\includegraphics[width=0.5\textwidth]{optimalsizingprocess2}
\centering
\caption{Comparative of optimal sizing methods. \textcolor{red}{could you please convert this figure into greyscale?}}
\label{fig:optimization}
\end{figure}
